---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```
# pkgr.utils

<!-- badges: start -->
<!-- badges: end -->

The goal of `pkgr.utils` is to control `pkgr` with utility functions from within `R`.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pkgr.utils)
```

### Command line builders

add/remove packages to `pkgr.yml`

```{r}
pkgs <- c('dplyr','ggplot2')

pkgs%>%
  pkgr.add()

pkgs%>%
  pkgr.add(config='pkgr.yml')

pkgs%>%
  pkgr.add(config='pkgr.yml',flags='install')

pkgs[1]%>%
  pkgr.remove()
```

plan/install

```{r}
# basic
pkgr.plan()
pkgr.install()


# with options
pkgr.install(config='pkgr.yml',library=.libPaths()[1])

# using pkgr.here function
pkgr.install(config=pkgr.here(),library=.libPaths()[1])

```

### Initialize a yml from a template

```{r}
pkgs%>%
  pkgr.utils::pkgr.new()
```

### Convert DESCRIPTION file to pkgr.yml

#### Local

```{r}

pkgr.utils::get_deps()%>%
  pkgr.utils::pkgr.new()

```

#### URL

```{r}
sinew_uri <- 'https://raw.githubusercontent.com/metrumresearchgroup/sinew/master/DESCRIPTION'

sinew_uri%>%
  pkgr.utils::get_deps()%>%
  pkgr.utils::pkgr.new()
```

### Convert pkgSetup.R file to pkgr.yml

```{r}

system.file('pkgSetup.R',package = 'pkgr.utils')%>%
  pkgr.utils::get_deps(type = 'pkgSetup')%>%
  pkgr.utils::pkgr.new(
    repos = c(pkgsetup = 'pkg',pkgr.utils::get_repos()),
    libpath = 'lib'
  )

```

### Find difference in packages listed in DESCRIPTION/pkgSetup and pkgr.yml

#### pkgSetup.R

```{r}
tf <- tempfile(fileext = '.yml')

pkgr.utils::get_deps(type = 'DESCRIPTION')%>%
  pkgr.utils::pkgr.new(
    repos = c(pkgsetup = 'pkg',pkgr.utils::get_repos()),
    libpath = 'lib',
    out = tf
  )

pkgr.utils::pkgr.diff(
  src = system.file('pkgSetup.R',package = 'pkgr.utils'),
  pkgr = tf
)

```

#### DESCRIPTION

```{r}

pkgr.utils::pkgr.diff(src = 'DESCRIPTION',pkgr = tf)

pkgr.utils::pkgr.diff(src = sinew_uri,pkgr = tf)

```
