---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```
# pkgr.utils

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `pkgr.utils` is to create `pkgr` commands and config files from templates from within `R`.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pkgr.utils)
```

### Updating/Installing pkgr with pkgr.utils

`Use_pkgr()` checks the OS that R is being used on and returns installation instructions for pkgr on the system. It also checks if the current release is installed on the system. If it is not then the user is asked if the steps listed should be executed to update to the current release.

```{r}
pkgr.utils::use_pkgr()
```


### Command line builders

> To run these outputs from within `R` pipe (`%>%`) them into a `system` call.

add/remove packages to `pkgr.yml`

```{r}
pkgs <- c('dplyr','ggplot2')

pkgs%>%
  pkgr.add()

pkgs%>%
  pkgr.add(config='pkgr.yml')

pkgs%>%
  pkgr.add(config='pkgr.yml',flags='install')

pkgs[1]%>%
  pkgr.remove()
```

plan/install

```{r}
# basic
pkgr.plan()
pkgr.install()


# with options
pkgr.install(config='pkgr.yml',library=.libPaths()[1])

# using pkgr.here function
pkgr.install(config=pkgr.here(),library=.libPaths()[1])

```

### Initialize a yml from a template

```{r}
pkgs%>%
  pkgr.utils::pkgr.new()
```

### Convert DESCRIPTION file to pkgr.yml

#### Local

```{r}

pkgr.utils::get_deps()%>%
  pkgr.utils::pkgr.new()

```

#### URL

```{r}
sinew_uri <- 'https://raw.githubusercontent.com/metrumresearchgroup/sinew/master/DESCRIPTION'

sinew_uri%>%
  pkgr.utils::get_deps()%>%
  pkgr.utils::pkgr.new()
```

### Convert pkgSetup.R file to pkgr.yml

```{r}

system.file('pkgSetup.R',package = 'pkgr.utils')%>%
  pkgr.utils::get_deps(type = 'pkgSetup')%>%
  pkgr.utils::pkgr.new(
    repos = c(pkgsetup = 'pkg',pkgr.utils::get_repos()),
    libpath = 'lib'
  )

```

### Find difference in packages listed in DESCRIPTION/pkgSetup and pkgr.yml

#### pkgSetup.R

```{r}
tf <- tempfile(fileext = '.yml')

pkgr.utils::get_deps(type = 'DESCRIPTION')%>%
  pkgr.utils::pkgr.new(
    repos = c(pkgsetup = 'pkg',pkgr.utils::get_repos()),
    libpath = 'lib',
    out = tf
  )

pkgr.utils::pkgr.diff(
  src = system.file('pkgSetup.R',package = 'pkgr.utils'),
  pkgr = tf
)

```

#### DESCRIPTION

```{r}

pkgr.utils::pkgr.diff(src = 'DESCRIPTION',pkgr = tf)

pkgr.utils::pkgr.diff(src = sinew_uri,pkgr = tf)

```
